---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
options(tibble.print_min = 5, tibble.print_max = 5)
```

# demoR

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/demoR)](https://cran.r-project.org/package=demoR)

## Overview

demoR is a set of tools for formatting `R` code for presentations, teaching demonstrations, and much more:

* The `hlt_*()` functions add text display formatting to printed code.

* The `demo_*()` functions print and run the code.

These combine naturally within code chunks in R Markdown files via code chunk options. You can learn more about them in `vignette("demoR")`.

## Installation

```{r, eval = FALSE}
# The easiest way to get demoR is the basic installation:
install.packages("demoR")
```

### Development version

To get a bug fix, or use a feature from the development version, you can install 
dplyr from GitHub.

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("kbodwin/demoR")
```


## Usage

```{r, message = FALSE}
library(demoR)
data(iris)
codestring <- "mean(iris$Sepal.Length)"

hlt_funs(codestring)

hlt_args(codestring)
```

## Getting help

If you encounter a clear bug, please file a minimal reproducible example on [github](https://github.com/kbodwin/demoR/issues). For questions and other discussion, please use [community.rstudio.com](https://community.rstudio.com/), or the [manipulatr mailing list](https://groups.google.com/group/manipulatr).

---

