---
title: "Presenting your code with demoR"
author: "Kelly Bodwin"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE
)
```

When teaching programming or presenting software in R, you may want to:
* visually highlight portions of code
* compare the effects of small changes to source code
* prompt learners to make their own modifications to code snippets and see the results

The `demoR` package is designed to streamline these tasks in R Markdown and its add-ons.  It consists of three sets of functions:

1.  `highlight` functions for easy coloring of code to be both run and displayed.
2.  `compare` functions for toggling options in a code string and comparing output.
3.  `teach` functions for accepting and executing dynamic code input.

This vignette will discuss the use of the first two suites of functions.  (`teach` functions require R Markdown with prerendered Shiny; these are summarized in their own vignette.)

## Code Highlighting

```{r}
data(iris)
codestring <- "mean(iris$Sepal.Length)"

hlt_funs(codestring)

hlt_args(codestring)

hlt_specific(codestring, "iris", color = "blue")
```


## Option Comparing

```{r}
code_string <- "ggplot(data = mtcars, aes(x = mpg, y = disp)) + geom_point()"
aes_option <- "color = cyl"

ggcompare(code_string, aes_option)
```


